Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-04-28 博士/论文提交/adversarial_attack/TCSVT/latex/imperceptible.tex
粘贴改相加

% 摘要
\begin{abstract}
Siamese trackers are shown to be vulnerable to adversarial attacks recently. However, the existing attack methods craft the perturbations for each video independently, which comes at a non-negligible computational cost. In this paper, we show the existence of universal perturbations that can enable the targeted attack, e.g., forcing a tracker to follow the ground-truth trajectory with specified offsets, to be video-agnostic and free from inference in a network. Specifically, we attack a tracker by adding a universal imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., a small universal adversarial patch, into the search images adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our approach allows perturbing a novel video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimisation or network inference. Experimental results on several datasets demonstrate that our approach can effectively fool the Siamese trackers in a targeted attack manner. The proposed method can also perform black box attack on different tracking architectures. We will make our code publicly available.
\end{abstract}

@@

In this paper, we make the first attempt in finding the universal perturbations (Figure \ref{fig:UAP}) that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal imperceptible perturbation to the template image and pasting a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.7\textwidth]{images_imperceptible/network_v5.pdf}
  \caption{The training pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the \textit{fake target} $p$ into $\textbf x$, the tracker outputs the location and size of the \textit{fake target} instead of the real target.}
  \label{fig:net}
\end{figure*}

@@

Targeted attacks to follow an erroneous path which looks realistic are crucial to deceive the tracking system without raising any suspicion in the real-world applications.
SPARK \cite{SPARK} computes incremental perturbations by using information from the past frames to perform targeted attacks to Siamese trackers. However, SPARK needs to generate distinct adversarial examples for every search image through heavy iterative schemes, which is time-consuming to attack online-tracking in real time. The recent real-time attacker in \cite{TTP} exclusively uses the template image to generate temporally-transferable perturbation in a one-shot manner, and then adds it to every search image. However, this method still needs to generate perturbations for each individual video, and its targeted attack setting requires diverse perturbations from several runs of network inference. It is ill-suited to attack a real-world online-tracking system when we can not get access to the limited computational resources. In this paper, however, we propose video-agnostic perturbations which allow perturbing a novel video to come at no additional cost except the mere addition and pasting operations.

@@

In this section, we introduce our video-agnostic targeted attack framework for Siamese trackers. We aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., an adversarial patch, into the search images adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Below, we formalize our targeted attacks to SiamFC++ \cite{SiamFC++}, and then introduce our perturbation strategy in detail.

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x_i$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ into $\textbf x_i$, the tracker outputs the location and size of the adversarial patch instead of the real target (see Figure \ref{fig:net}). Both $\delta$ and $p$ are universal (\ie, video-agnostic), which means perturbing a novel video only involves the mere addition and pasting of the perturbations to the template and search images -- and does not require gradient optimisation or network inference.

@@

In this subsection, we show how to train the video-agnostic perturbations $(\delta, p)$ for Siamese trackers (Figure \ref{fig:vis_perturbations}). At beginning, each element in $\delta$ is initialized to 0. $p$ is initialized with a normal distribution, with a mean of 127 and a standard deviation of 1. During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick paired frames $I_t, I_s$ from $V$. The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_k.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a \textit{fake target} and pasted into the search images. We force the center position of the \textit{fake target} to near the center position of the real target within a shift range of 64 pixels, where shift is defined as the maximum range of translation generated from a uniform distribution.
The width/height of the \textit{fake target} is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, \{x_0, y_0, x_1, y_1\}),
\end{equation}
where $ \hat b^{fake} = \{x_0, y_0, x_1, y_1\}$ denote the coordinates of the upper-left and lower-right corners of the fake target on the search image. $A$ is a patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{(x_1-x_0)\times (y_1-y_0)\times 3}$, and then pastes the resized patch $\hat{p}_k$ into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$. Subsequently, the SiamFC++ tracker takes $\tilde {\textbf x}$ and $\tilde{\textbf z}$ as input and predicts $\textbf{C, R, Q}$ in an anchor-free manner.

@@

Once the perturbations $(\delta, p)$ are trained, we can use them to perturb the template image and search images of any novel video for attacking. Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a novel video only involves the mere addition and pasting of the perturbations to the template and search images -- and does not require gradient optimisation or network inference.
Assume $B^{fake}=\{b^{fake}_i\}_1^{T}$ is the trajectory we hope the tracker to output.
During tracking the $i$-th frame of the video $V=\{I_i\}_1^T$, we need to transform the bounding box $b^{fake}_i$ (with respect to the original frame $I_i$) into the box $\hat b^{fake}_i=\{x_{0_i}, y_{0_i}, x_{1_i}, y_{1_i}\}$ with respect to the search image $\textbf x_i$, and paste $p$ into $\textbf x_i$ according to $\hat b^{fake}_i$:
\begin{equation}
\tilde{\textbf x}_i = A(\textbf x_i, p, \{x_{0_i}, y_{0_i}, x_{1_i}, y_{1_i}\}).
\end{equation}
The tracker then takes $\tilde{\textbf z}_i=\textbf z_i+\delta$ and $\tilde{ \textbf x}_i$ as input, and the subsequent tracking procedure remains the same as SiamFC++.

@@

\textit{Generating the Fake Trajectory} We need to predefine a specific trajectory $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video to achieve targeted attack in the online-tracking phase, which we call the \textit{fake trajectory}. We denote the \textit{real trajectory} as $B^{gt}=\{b^{gt}_i\}_1^T$ with the bounding box ground truth.
It is possible to manually label arbitrary $B^{fake}$ for each video, however, it will be time-consuming in our experimental evaluation. So we generate $B^{fake}$ based on $B^{gt}$. Specifically, the \textit{fake trajectory} follows the \textit{real trajectory} and the adjacent boundaries of $b^{fake}_i$ and $b^{gt}_i$ are 16 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the \textit{fake trajectory} gradually changes from the size of $b^{gt}_1$ to $64\times 64$ (Figure \ref{fig:vis}). Because the annotations of GOT-10k's test data are kept private, we only use its validation set for our evaluation and denote it as GOT-Val. Note that the target position of the first frame is pre-defined in the academic study of object tracking, while in practical application, the target position of the first frame is often obtained by running an object detector on this frame. In this scenario, once the target position of the first frame is obtained, we can put the adversarial patch near the target to mislead the tracker. In the next frames, we can specify an arbitrary \textit{fake trajectory} to place the adversarial patch.

@@

In our evaluation, the backbone Siamese network of our base tracker SiamFC++ \cite{SiamFC++} adopts GoogLeNet \cite{GoogLeNet}.
We implement our approach in Pytorch and train our perturbations using three GTX 1080Ti GPUs.
We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set.
We train the perturbations for 32768 iterations with a mini-batch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and for the adversarial patch it is $\epsilon_2 = 0.5$.
We generate training samples following the practice in SiamFC++.
During both the training and online-tracking phase, the off-the-shelf SiamFC++ tracking network model\footnote{It is exclusively trained on the training split of GOT-10k by the authors of SiamFC++ and can be downloaded from \url{https://drive.google.com/file/d/1BevcIEZr_kgyFjhxayOFw08DFl2u5Zi7/view}} is fixed and used for the whole evaluation, the spatial size of the template image is set to $127\times 127$, and the search image is $303\times 303$.
In Equ. \ref{eq:loss}, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005$, and $\sigma=10^{-5}$.

@@

We compare the attack method proposed in this paper with the latest attack methods, including the AlexNet-based untargeted attack method CSA \cite{CSA}, and two other targeted attack methods: the AlexNet-based FAN \cite{FAN} and the ResNet50-based TTP \cite{TTP} (Figure \ref{fig:SOTA}). We report the accuracy scores with respect to the real/fake trajectories in table \ref{tab:SOTA}. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding the box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, so the attack time is as high as 4720 ms, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation and the image paste operation to generate adversarial information for any video without gradient optimization or network inference.

@@

In this paper, we propose a video-agnostic targeted attack method for Siamese trackers. 
We aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, \ie, a small adversarial patch, into the search image adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.
Experiments on several popular datasets show that our method can effectively fool the Siamese trackers in a targeted attack manner.

@@

\begin{IEEEbiography}
{YaYa Shi}
received the B.S. degree from the Hefei University of Technology, Anhui, China in 2018. Currently, She is a Ph.D. student with the University of Science and Technology of China, Anhui, China. Her research interests include video captioning and deep learning.
\end{IEEEbiography}

\begin{IEEEbiography}
{Shaoru Wang}
???
\end{IEEEbiography}

>>>>

% 摘要
\begin{abstract}
Siamese trackers are shown to be vulnerable to adversarial attacks recently. However, the existing attack methods craft the perturbations for each video independently, which comes at a non-negligible computational cost. In this paper, we show the existence of universal perturbations that can enable the targeted attack, e.g., forcing a tracker to follow the ground-truth trajectory with specified offsets, to be video-agnostic and free from inference in a network. Specifically, we attack a tracker by adding a universal imperceptible perturbation to the template image and adding a \textit{fake target}, i.e., a small universal adversarial patch, into the search images adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our approach allows perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimisation or network inference. Experimental results on several datasets demonstrate that our approach can effectively fool the Siamese trackers in a targeted attack manner. The proposed method can also perform black box attack on different tracking architectures. We will make our code publicly available.
\end{abstract}

@@

In this paper, we make the first attempt in finding the universal perturbations (Figure \ref{fig:UAP}) that fool a state-of-the-art Siamese tracker, \ie, SiamFC++ \cite{SiamFC++}, in a targeted attack manner, which comes at virtually no cost in the online-tracking phase. Specifically, we aim to attack the trackers by adding a universal imperceptible perturbation to the template image and adding a \textit{fake target}, \ie, a small universal adversarial patch, into the search image adhering to the predefined trajectory (as shown in Figure \ref{fig:1}), so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Our generated video-agnostic perturbations allow perturbing a novel video to come at no additional cost except the mere addition operations -- and not require gradient optimization or network inference. Experiment results on OTB2015 \cite{OTB}, GOT-10k \cite{GOT-10k} and LaSOT \cite{GOT-10k} benchmarks demonstrate the effectiveness and efficiency of our approach.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.7\textwidth]{images_imperceptible/network_v5.pdf}
  \caption{The training pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and adding the \textit{fake target} $p$ into $\textbf x$, the tracker outputs the location and size of the \textit{fake target} instead of the real target.}
  \label{fig:net}
\end{figure*}

@@

Targeted attacks to follow an erroneous path which looks realistic are crucial to deceive the tracking system without raising any suspicion in the real-world applications.
SPARK \cite{SPARK} computes incremental perturbations by using information from the past frames to perform targeted attacks to Siamese trackers. However, SPARK needs to generate distinct adversarial examples for every search image through heavy iterative schemes, which is time-consuming to attack online-tracking in real time. The recent real-time attacker in \cite{TTP} exclusively uses the template image to generate temporally-transferable perturbation in a one-shot manner, and then adds it to every search image. However, this method still needs to generate perturbations for each individual video, and its targeted attack setting requires diverse perturbations from several runs of network inference. It is ill-suited to attack a real-world online-tracking system when we can not get access to the limited computational resources. In this paper, however, we propose video-agnostic perturbations which allow perturbing a novel video to come at no additional cost except the mere addition operations.

@@

In this section, we introduce our video-agnostic targeted attack framework for Siamese trackers. We aim to attack the tracker by adding an imperceptible perturbation to the template image and adding a \textit{fake target}, i.e., an adversarial patch, into the search images adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Below, we formalize our targeted attacks to SiamFC++ \cite{SiamFC++}, and then introduce our perturbation strategy in detail.

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x_i$. After adding $\delta$ to $\textbf z$ and adding the fake target $p$ into $\textbf x_i$, the tracker outputs the location and size of the adversarial patch instead of the real target (see Figure \ref{fig:net}). Both $\delta$ and $p$ are universal (\ie, video-agnostic), which means perturbing a novel video only involves the mere addition of the perturbations to the template and search images -- and does not require gradient optimisation or network inference.

@@

In this subsection, we show how to train the video-agnostic perturbations $(\delta, p)$ for Siamese trackers (Figure \ref{fig:vis_perturbations}). At beginning, each element in $\delta$ is initialized to 0. $p$ is initialized with a normal distribution, with a mean of 127 and a standard deviation of 1. During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick paired frames $I_t, I_s$ from $V$. The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_k.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a \textit{fake target} and added into the search images. We force the center position of the \textit{fake target} to near the center position of the real target within a shift range of 64 pixels, where shift is defined as the maximum range of translation generated from a uniform distribution.
The width/height of the \textit{fake target} is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, \{x_0, y_0, x_1, y_1\}),
\end{equation}
where $ \hat b^{fake} = \{x_0, y_0, x_1, y_1\}$ denote the coordinates of the upper-left and lower-right corners of the fake target on the search image. $A$ is a patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{(x_1-x_0)\times (y_1-y_0)\times 3}$, and then adds the resized patch $\hat{p}_k$ into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$. Subsequently, the SiamFC++ tracker takes $\tilde {\textbf x}$ and $\tilde{\textbf z}$ as input and predicts $\textbf{C, R, Q}$ in an anchor-free manner.

@@

Once the perturbations $(\delta, p)$ are trained, we can use them to perturb the template image and search images of any novel video for attacking. Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a novel video only involves the mere addition of the perturbations to the template and search images -- and does not require gradient optimisation or network inference.
Assume $B^{fake}=\{b^{fake}_i\}_1^{T}$ is the trajectory we hope the tracker to output.
During tracking the $i$-th frame of the video $V=\{I_i\}_1^T$, we need to transform the bounding box $b^{fake}_i$ (with respect to the original frame $I_i$) into the box $\hat b^{fake}_i=\{x_{0_i}, y_{0_i}, x_{1_i}, y_{1_i}\}$ with respect to the search image $\textbf x_i$, and add $p$ into $\textbf x_i$ according to $\hat b^{fake}_i$:
\begin{equation}
\tilde{\textbf x}_i = A(\textbf x_i, p, \{x_{0_i}, y_{0_i}, x_{1_i}, y_{1_i}\}).
\end{equation}
The tracker then takes $\tilde{\textbf z}_i=\textbf z_i+\delta$ and $\tilde{ \textbf x}_i$ as input, and the subsequent tracking procedure remains the same as SiamFC++.

@@

\textit{Generating the Fake Trajectory} We need to predefine a specific trajectory $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video to achieve targeted attack in the online-tracking phase, which we call the \textit{fake trajectory}. We denote the \textit{real trajectory} as $B^{gt}=\{b^{gt}_i\}_1^T$ with the bounding box ground truth.
It is possible to manually label arbitrary $B^{fake}$ for each video, however, it will be time-consuming in our experimental evaluation. So we generate $B^{fake}$ based on $B^{gt}$. Specifically, the \textit{fake trajectory} follows the \textit{real trajectory} and the adjacent boundaries of $b^{fake}_i$ and $b^{gt}_i$ are 2 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the \textit{fake trajectory} gradually changes from the size of $b^{gt}_1$ to $64\times 64$ (Figure \ref{fig:vis}). Because the annotations of GOT-10k's test data are kept private, we only use its validation set for our evaluation and denote it as GOT-Val. Note that the target position of the first frame is pre-defined in the academic study of object tracking, while in practical application, the target position of the first frame is often obtained by running an object detector on this frame. In this scenario, once the target position of the first frame is obtained, we can put the adversarial patch near the target to mislead the tracker. In the next frames, we can specify an arbitrary \textit{fake trajectory} to place the adversarial patch.

@@

In our evaluation, the backbone Siamese network of our base tracker SiamFC++ \cite{SiamFC++} adopts GoogLeNet \cite{GoogLeNet}.
We implement our approach in Pytorch and train our perturbations using three GTX 1080Ti GPUs.
We adopt COCO \cite{COCO}, ILSVRC-VID \cite{VID} and the training splits of GOT-10k \cite{GOT-10k} and LaSOT \cite{LaSOT} as our training set.
We train the perturbations for 32768 iterations with a mini-batch of 96 images (32 images per GPU).
The learning rate of the template perturbation $\epsilon_1$ is set to 0.1, and for the adversarial patch it is $\epsilon_2 = 0.5$.
We generate training samples following the practice in SiamFC++.
During both the training and online-tracking phase, the off-the-shelf SiamFC++ tracking network model\footnote{It is exclusively trained on the training split of GOT-10k by the authors of SiamFC++ and can be downloaded from \url{https://drive.google.com/file/d/1BevcIEZr_kgyFjhxayOFw08DFl2u5Zi7/view}} is fixed and used for the whole evaluation, the spatial size of the template image is set to $127\times 127$, and the search image is $303\times 303$.
In Equ. \ref{eq:loss}, we set $\alpha=1, \beta=1, \gamma=1, \eta=0.005$, and $\sigma=0.005$.

@@

We compare the attack method proposed in this paper with the latest attack methods, including the AlexNet-based untargeted attack method CSA \cite{CSA}, and two other targeted attack methods: the AlexNet-based FAN \cite{FAN} and the ResNet50-based TTP \cite{TTP} (Figure \ref{fig:SOTA}). We report the accuracy scores with respect to the real/fake trajectories in table \ref{tab:SOTA}. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding the box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, so the attack time is as high as 4720 ms, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.

@@

In this paper, we propose a video-agnostic targeted attack method for Siamese trackers. 
We aim to attack the tracker by adding an imperceptible perturbation to the template image and adding a \textit{fake target}, \ie, a small adversarial patch, into the search image adhering to the predefined trajectory, so that the tracker outputs the location and size of the \textit{fake target} instead of the real target. Being universal, the generated perturbations can be conveniently exploited to perturb videos on-the-fly without extra computations.
Experiments on several popular datasets show that our method can effectively fool the Siamese trackers in a targeted attack manner.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images_imperceptible/author/yyshi.png}}]
{YaYa Shi}
received the B.S. degree from the Hefei University of Technology, Anhui, China in 2018. Currently, She is a Ph.D. student with the University of Science and Technology of China, Anhui, China. Her research interests include video captioning and deep learning.
\end{IEEEbiography}

\begin{IEEEbiography}
{Shaoru Wang}
received the B.E. degree from Department of School of Information and Communication Engineering in Beijing University of Posts and Telecommunications, Beijing, China in 2018. He is currently pursuing his Ph.D. degree in the Institute of Automation, Chinese Academy of Sciences (CASIA), Beijing, China. His current research interests include computer vision and deep learning.
\end{IEEEbiography}
